---
title: "Socks"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Socks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Load up **InteractiveTradeR**
```{r setup}
library(InteractiveTradeR)
```

## A Word on Connection Parameters
When you first load **InteractiveTradeR**, you'll be asked if you want to store
some default connection parameters. It is recommended that you do so; this will
create a ".Rprofile" file (or will add to the existing one, if there is one) in
your RStudio project home directory. .Rpofile contains the port numbers, 
hostname, etc that **InteractiveTradeR** will use to connect to the API.

If you prefer, you can configure these yourself on a session-by-session basis.
The parameters are stored as R options and can be set like this:
```{r}
options(interactivetrader.platform         = "TWS")
options(interactivetrader.paper            = TRUE)
options(interactivetrader.tws.paper.host   = "localhost")
options(interactivetrader.tws.paper.port   = 7497)
options(interactivetrader.tws.paper.master = 57869)
```

Note that if you're connecting to a **LIVE** (non-paper) IB account without 
permission, you're violating the licence agreement!

## Open your Connections Window in TWS/IBG
This vignette is a lot more informative if you pull up the "Connections" window
in TWS/IBG alongside RStudio as you run the examples yourself. In IB Gateway,
the connections info is displayed in the default GUI; in TWS, you can find it by
clicking on the "DATA" text in the upper right-hand corner of the window.
Keeping an eye on the API connections will help you understand how
**InteractiveTradeR** communicates with the IB apps.

## Sync Mode
If you're just interested in running a script or pinging IB for info every now
and then, you don't really need to worry about **Async Mode** and can just stick
to the "there-and-back-again" **Sync Mode**, which is the default for all 
**InteractiveTradeR** functions that communicate with IB.

For example, if you call \link{req_current_time}() on its own, it'll open up a
socket, ask IB for the time, get the response, and then close the socket behind
itself when it's finished.

```{r}
# Sync Mode:
req_current_time()
```

If you're following along in the Connections window of IBG/TWS, you should note
that a new connection was briefly created, then closed as you ran the above.

## Async Mode
**Sync Mode** is convenient and simple, but if you're building a Shiny app,
dashboard, or an online trading program, you're going to need the ability to
create subscriptions to data feeds like open orders, account balances, P/L, and
so on. These values update asynchronously; for example, if you've placed an
active limit order, there is no way for you to be sure when/if the order fills.

All **InteractiveTradeR** functions that communicate with IB can also be used in
**Async Mode**, in which you create a persistant socket object that is not
opened & closed each time a function executes. \link{req_current_time}(), for
example, can be called in **Async Mode** as follows:

```{r}
# Async Mode:
create_new_connections()             #1. Create a new sock
#socks()                              #2. View your socks (optional, of course)
req_current_time(channel = "async")  #3. Use sock to req_current_time()
disconnect()                         #4. Close the sock when you're finished.
```
